Classless Java

### 2015-11-15 paper/sections/CaseStudy.tex
text for Game case study

\paragraph{\textbf{Initial System}}
The initial system expresses arithmetic expressions with only literals and
addition structure:

@@

\paragraph{\textbf{Adding a New Variant}} 
It is easy to add new data variants to the code in the initial system in a
modular way. For example, the following code how to add the subtraction variant.

@@

\paragraph{\textbf{Adding a New Operation}}
Adding new operations to the previous system is still straightforward (although
requires longer code). The following code shows an example of adding a new
operation \texttt{print}.

@@

>>>>

\subsubsection{Initial System}
The initial system expresses arithmetic expressions with only literals and
addition structure:

@@

\subsubsection{Adding a New Variant}
It is easy to add new data variants to the code in the initial system in a
modular way. For example, the following code how to add the subtraction variant.

@@

\subsubsection{Adding a New Operation}
Adding new operations to the previous system is still straightforward (although
requires longer code). The following code shows an example of adding a new
operation \texttt{print}.

@@

\subsection{A Small Game Example}
We now present a variant of a classic game example, which is often used to
evaluate reuse ability related to inheritance and design patterns. The code
using our approach and the solution by Bono et. al~\cite{bono14} in online, for
space constraints, we will omit it here. In the game, there is a player with the
goal of collecting as many coins as possible. She may enter a room with several
doors to be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different features and
behaviour), multiple inheritance (a special kind of door may require features
from two other door types). It also shows how to model symmetric sum, override
and alias as trait-oriented programming. Moreover, the code is provided in
~\cite{bono14} so that we can have a clear and fair comparison with our
approach, as shown in Table~\ref{table:codereduction}.

\begin{table}[h]
\centering
\begin{tabular}{ccc}
\hline
            & SLOC   & \# of classes/interfaces \\ \hline
Bono et al. & 335    & 14                       \\
Ours        & 199    & 11                       \\
\rowcolor[HTML]{C0C0C0} 
Reduced by  & 40.6\% & 21.4\%                   \\ \hline
\end{tabular}
\caption{Code Reduction and Reuse.}
\label{table:codereduction}
\end{table}
